Trends of SDR in Thessaloniki

### 2023-06-12 Article_B141.Rmd
B141

## Trends by SZA

.........

@@

See Figures \ref{fig:szatrends}a and \ref{fig:szatrends}b

```{r szatrends, echo = FALSE, fig.cap='two plots', fig.subcap=c('one plot', 'the other one'), out.width='.35\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics(c("./images/SzaTrends-13.pdf", "./images/SzaTrends-21.pdf"))
```

@@

Similar we have produced the deseasonalized trend for different sky conditions for each season of the year, using the corresponding mean monthly values.

@@

@@

.........

@@

>>>>

## Long term trends by Solar zenith angle.

Analyzing the long term trends of SDR to bins of SZA, we can see the contribution of the geometry and time in a diurnal level (Figures \ref{fig:szatrends}a and \ref{fig:szatrends}b). Although there is a seasonal distribution of SZA than in not presented here.

@@

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.34\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics(c("./images/SzaTrends-13.pdf", "./images/SzaTrends-21.pdf"))
```

@@

Similar we have produced the deseasonalized trend for different sky conditions for each season of the year, using the corresponding mean monthly values.
This can give us a better understanding of the annual variability of the trends.

@@

......

NOT INCLUDE?

@@

@@

Figure \ref{fig:cumsum}
